Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-23 article.rnw
Swap some secions in the methods around.
The model is more important than the phylogeny, and should come first.
Remove an extraneous comma.

\subsubsection{Phylogeny}

I determined the phylogenetic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.

>>>>

\subsection{Phylogeny}

I determined the phylogenetic relationships between the six study species by examination of the literature, in order to compare these to the groupings generated by the models.
No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.
